Learning to Prove with Tactics

### 2018-03-28 presentation/presentation.tex
reconstruction

Goal appearing during proof search:
\begin{lstlisting}[language=SMLSmall]
LENGTH (MAP f l) = LENGTH l
\end{lstlisting}

@@

\begin{frame}{Re-proving: results}
Evaluation is "fair". (not totally if you ask Freek)\\
Only previous proofs are available for training.

@@

\begin{frame}{Re-proving: number of proofs found in less that x seconds}
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\}

@@

\begin{frame}{Re-proving: number of human proofs of size x}
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, red!100\\
solid, mark repeat=100, mark phase=0, blue!100\\}

\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.3*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=2000,
  xmin=0, xmax=15,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.6*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=100,
  xmin=15, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\legend{\holfour,\cakeml}
\end{axis}
\end{tikzpicture}
\end{frame}

\begin{frame}{Re-proving: percentage of proof of size x solved}
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\}

@@

Advantages over ATPs (\eprover) for ITP (\holfour) users:
\begin{itemize}
\item Includes domain specific automation found in the ITP.
\item Generated proofs are human-level proofs.\\
\item No reconstruction needed.\\
\end{itemize}

>>>>

\vspace{10mm}

New goal appearing during proof search:
\begin{lstlisting}[language=SMLSmall]
LENGTH (MAP f l) = LENGTH l
\end{lstlisting}

@@

\begin{frame}{Re-proving: results}
Evaluation is "fair". (not totally if you ask Freek)\\\ \ 
Only previous proofs are available for training.\\\ \
\tactictoe does not call external provers.\\

@@

\begin{frame}{Re-proving: proofs of size x}
\pgfplotscreateplotcyclelist{my black}{
solid, red!100\\
solid, blue!100\\
dashed, red!100\\
dashed, blue!100\\
}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.3*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=2000,
  xmin=0, xmax=15,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_proof_length};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.7*\textwidth,
  height=0.7*\textwidth,
  ymin=0, ymax=100,
  xmin=15, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/original_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_original_proof_length};
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/cakeml_proof_length};
\legend{\holfour,\cakeml,\tactictoe in \holfour,\tactictoe in \cakeml}
\end{axis}
\end{tikzpicture}
\end{frame}

\begin{frame}{Re-proving: \holfour proofs found in less than x 
seconds}
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\}

@@

\begin{frame}{Re-proving: percentage of solved \holfour proof of size x }
\pgfplotscreateplotcyclelist{my black}{
solid, mark repeat=100, mark phase=0, black!100\\
dashed, mark repeat=100, mark phase=0, black!100\\}

@@

Advantages over ATPs (\eprover) for ITP (\holfour) users:
\begin{itemize}
\item Includes domain specific automation found in the ITP.
\item Generated proofs are human-level proofs.\\
\item No translation or reconstruction needed.\\
\end{itemize}
